Differentially Private Bayesian Inference

### 2018-04-20 main.tex
update

\subsection{Accuracy Study Based on L1 Norm Distance}
For comparison, we study the accuracy of these four mechanisms based on l1 norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$, shown in Fig. \ref{fig_dirichlet_hellinger_l1}.

\begin{figure*}
\begin{center}
\centering
  \subfigure[accuracy measurement based on Hellinger distance]{
    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_hellinger.eps}}
  \subfigure[accuracy measurement based on l1 norm]{
    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_l1.eps}} 
\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance and l1 norm, where data size $n = 150$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP}
\label{fig_dirichlet_hellinger_l1}
\end{center}
\end{figure*}

>>>>

\subsection{Accuracy Study Based on $L_1$ Norm Distance}
For comparison, we study the accuracy of these four mechanisms based on $l_1$ norm, with the Dirichlet distribution $\dirichlet(7,4,5)$ and data size $150$, shown in Fig. \ref{fig_dirichlet_hellinger_l1}.

\begin{figure*}
\begin{center}
\centering
  \subfigure[accuracy measurement based on Hellinger distance]{
    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_hellinger.eps}}
  \subfigure[accuracy measurement based on $l_1$ norm]{
    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_l1.eps}} 
\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance and $l_1$ norm, where data size $n = 150$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP}
\label{fig_dirichlet_hellinger_l1}
\end{center}
\end{figure*}
